Teaching a Class to Grade Itself

### 2013-09-02 Primes Write up.tex
Some edits

\documentclass[12pt, Helvetica]{article}   	
\title{Primes Paper}
\author{Nick Kaashoek and William Wu}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Corsera or EdX are well funded, which explains their rapid growth: EdX is funded by 60 million dollars\cite{canmoocsreducecc}. However, the MOOC's main importance comes from it's scalability. Moocs are able to educate massive numbers of students from anywhere in the world\cite{makingsenseofmoocs}: In Coursera alone, there are 1.7 million students\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are unable to grade hundreds of thousands of sumbissions from a single homework assignment: a major problem. Currently, there are two ways to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers, severly limiting the depth of the questions asked\cite{rightandwrongmoocs}. On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be "hacked" by the students \cite{makingsenseofmoocs}. Although both of these systems are interesting concepts, they are unpolished and inefficient in practice.

The problem that we have located is important to solve. Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge. Because this limits their learning abilities, it is imperitive to create an efficient system that enables students to learn efficiently and grow. This is our goal.

@@

To efficiently prove a mathematical system such as we proposed, we need to lay out some tools first, chief among them being mechanism design and game theory. Without the correct tools, it is impossible to do the neccesary mathematical analysis on human behavior in these systems, so we turn to game theory. Game theory allows us to create a system of rules that have to be followed by everyone in the system. By manipulating these rules, we are able to change the behavior of everyone in the system. By adding basic assumptions about human nature, we are able to predict what will happen with a specific set of rules, and prove it; this will be how we prove and create our mechanism.

Our end goal with this project is to develop a mathematically provable and efficient mechanism to incentivize selfish people to accurately grade the assignments of others. By assuming that all the students in the system care about themselves, we assume that they are selfish. With this in mind, the problem becomes an issue of incentivization; how do we make these selfish people care about others? As such, our goal is to find the perfect incentive for these people. If we are succesful, this will make them grade the papers of others efficienly because they care, and fairly because they are human: this strikes the perfect balance between the two current solutions.

Mathematically provable systems like the one that we are trying to create always lead to good results. For example...

Some people might think that this is a rather simple problem to solve, and could come up with a variety of simple solutions that appear to be correct. Incentivizing people often seems simple at first; for example, why not just say "here, take this paper and grade it. I'll give you bonus points if you do it." Obviously, this will just return garbage because the students will just take the points and not care about the grading. The next step would be to implement some kind of simple checking: "here, you two students, take this paper and grade it. If you match, I'll give you bonus points." This case may seem like it works if the students are isolated, but smart students will just give the paper 100, not grade, match and get the points. Clearly, simple solutions aren't really that effective

As demonstrated by the above examples, this problem's complexity lies in the complex behavior of selfish human beings; as such, there is no simple way to solve it. Because human nature dictates that people will do whatever is in their best interests and will always try to outsmart the system, it quickly becomes apparent that a strict set of rules and assumptions is neccesary to dictate thier behavior. The rules, however, can never be to simple, because they need to anticipate every possible way the players (students) will attempt to outsmart them. This means that although we will try to create a relatively simple solution, it can never be to straightforward.

The complexity of human nature is what makes the problem interesting; this combined with its relevance makes it an interesting research oppurtunity. Although there may not be a simple and beautiful solution to this problem, our use of game theory to predict human nature provides tremendous grounds for interesting research. Not only does predicting human nature make this interesting, but the problem's relevance to modern times also means that this is a neccesary problem to solve, giving us good basis to design our solution on.

@@

\bibitem{canmoocsreducecc}
  http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
  Author,
  \emph{Title}.
  Source,
  Year.
  Ruth, S. (2012). Can MOOCís and existing e-learning paradigms help reduce college costs? International Journal of Technology in Teaching and Learning, 8(1), 21-32.

>>>>

\documentclass[12pt, Helvetica]{article}   	
\title{Teaching a Class to Grade Itself}
\author{Nick Kaashoek and William Wu}
\date{\today}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Corsera or EdX are well funded, which explains their rapid growth: EdX is funded by 60 million dollars~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from it's scalability. Moocs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: In Coursera alone, there are 1.7 million students~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are unable to grade hundreds of thousands of sumbissions from a single homework assignment: a major problem. Currently, there are two ways to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers, severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}. On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be "hacked" by the students ~\cite{makingsenseofmoocs}. Although both of these systems are interesting concepts, they are unpolished and inefficient in practice.

The problem that we have located is important to solve. Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge. Because this limits their learning abilities, it is imperative to create an efficient system that enables students to learn efficiently and grow. This is our goal.

@@

Without the correct tools, however, it is impossible to do the necessary mathematical analysis on such a system, so we first need to lay out our tools: game theory and mechanism design. Game theory allows us to create a unified system of assumptions that simulate a real classroom; this will tell us how the students behave. Then, we can use mechanism design to create a set of "rules" that the "players", the students, will have to follow; this is known as the mechanism. Using these assumptions and the rules we create, we can predict exactly how students will behave when they play our "game". Being able to predict what students will do allow us to prove the efficiency and effectiveness of our mechanism, allowing us to accomplish our goal.

Our end goal with this project is to develop a mathematically provable and efficient mechanism wherein people accurately grade the assignments of others. By assuming that all students in the system care about themselves, we assume that they are selfish. With this in mind, the problem becomes an issue of finding the right incentive; how do we make these selfish people care about others? As such, our goal is to find the perfect incentive for these people. If we are successful, this will make them grade the papers of others efficiently because they care, and fairly because they are human: this strikes the perfect balance between the two current solutions.

Some people might think that this is a rather simple problem to solve, and could come up with a variety of simple solutions that appear correct. Incentivizing people often seems simple at first; for example, why not just say "here, take this paper and grade it. I'll give you bonus points if you do it." Obviously, this will not return anything useful because the students will just take the points and not care about the grading. The next step would be to implement some kind of simple checking: "here, you two students, take this paper and grade it. If you match, I'll give you bonus points." This case may seem like it works if the students are isolated, but smart students will just give the paper 100, not grade, match and get the points. Clearly, simple solutions aren't really that effective.

As demonstrated by the above examples, this problem's complexity lies in the complex behavior of selfish human beings; as such, there is no simple way to solve it. Because human nature dictates that people will do whatever is in their best interests and will always try to outsmart the system, it quickly becomes apparent that a strict set of rules and assumptions are necessary to dictate their behavior. These rules, however, can never be too simple, because they need to anticipate every possible way the players (students) will attempt to outsmart them. This means that although we will try to create a relatively simple solution, it can never be too straightforward.

The complexity of human nature and the relevance that this problem has makes this an interesting research opportunity. Because it is so hard to predict human nature, our strategy for creating a solution provides an extremely interesting research opportunity, especially because it is something that no one else has attempted before. Also, the relevance of the problem we have located also makes this necessary research; thus making our solution even more interesting because it could actually be used in practice.

@@

\bibitem{canmoocsreducecc}
  http://sicet.org/journals/ijttl/issue1201/2_Ruth.pdf
  Author,
  \emph{Title}.
  Source,
  Year.
  Ruth, S. (2012). Can MOOCs and existing e-learning paradigms help reduce college costs? International Journal of Technology in Teaching and Learning, 8(1), 21-32.
